The Multi-Stencil Language

### 2016-05-30 ARTICLES/IJPP/article/evaluation.tex
allegement debut eval

This section presents evaluations of the work presented in this paper. First, the compiler is evaluated. Second, the data parallelization and fusion optimization are evaluated and compared to a full SkelGIS program. Third, the hybrid parallelization (data and task) is evaluated to validate the performance model detailed in Section~\ref{sect:tsp}.

All evaluations presented in this section are based on a real case study, the shallow-Water Equations. Navier-Stokes Equations is a well known set of partial differential equations in fluid dynamics to simulate a flow evolution in time. At the University of Orl\'eans, France, the MAPMO laboratory works on a software, called FullSWOF2D\footnote{\url{http://www.univ-orleans.fr/mapmo/soft/FullSWOF/}}, which solves the Shallow-Water Equations obtained from the three dimensional Navier-Stokes equations, by averaging on the vertical direction~\cite{Ferrari2004}. Those equations are solved using a two-dimensional Cartesian discretization of the space domain, and a finite volume numerical methods more described in~\cite{CPE:CPE3494}. We have developed a MSL version of FullSWOF2D that contains 3~mesh entities, 7~computation domains, 48~data and 98~computations (32~stencil kernels and 66~local kernels).

@@

Table~\ref{fig:exectime} illustrates the execution time for each step of the MSL compiler for an overall execution time of 4.6 seconds. Execution times have been computed on a laptop with a bi-core Intel Core i5 1.4~GHz, and 8~GB of DDR3. One can notice that the computation of the $TSP$ tree is the longest step of the compiler.

>>>>

This section evaluates the MSL compiler and the code it generates.
We first evaluate the generated code in the case where only data parallelization and fusion are applied and compare this to a full SkelGIS program.
Then, we analyze a case taking advantage of the full the hybrid parallelization combining data and task parallelism and validate the performance model proposed in Section~\ref{sect:tsp}.

All evaluations presented in this section are based on a real case study of the shallow-Water Equations as solved in  the FullSWOF2D\footnote{\url{http://www.univ-orleans.fr/mapmo/soft/FullSWOF/}}~\cite{Ferrari2004,CPE:CPE3494} code from the MAPMO laboratory, University of Orl\'eans.
We have developed a MSL version of FullSWOF2D that contains 3~mesh entities, 7~computation domains, 48~data and 98~computations (32~stencil kernels and 66~local kernels).

@@

Table~\ref{fig:exectime} illustrates the execution time for each step of the MSL compiler for the FullSWOF2D compiler.
This has been computed on a laptop with a bi-core Intel Core i5 1.4~GHz, and 8~GB of DDR3.
While the overall time of 4.6 seconds remains reasonable, one can notice that the computation of the $TSP$ tree is by far the longest step of the compiler.
As a matter of fact, the complexity of the algorithm for N-shapes removal is $O(n^3)$.
The replacement of the static scheduling by a direct scheduling of the DAG by dedicated tools should solve this in the future.
